---
title: "Simple document"
author: "Ruohan Lyu"
date: 2025-09-09
output: github_document
---
  
I'm an R Markdown document! 

```{r echo = TRUE, message = FALSE}
library(tidyverse)
```

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:
  
```{r}
samp = rnorm(100) # generate 100 random numbers from normal distribution
length(samp) # return to the number of elements
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

This is where I'm going to talk about code chunks.

```{r eval = FALSE}
mean(samp)
sd(samp)
```

Let's also make a dataframe.

```{r}
example_df =
   tibble(
     vec_numeric = 1:4,
     vec_char = c("My","name","is","Hannah"),
     vec_factor = factor(c("male","male","female","female"))
   )
```


Let's make a plot and see how cool it is!

```{r}
plot_df =
  tibble(
    x = rnorm(1000, mean = 1, sd = .5),
    y = 1 + 2 * x + rnorm(1000)
  )

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

This is a neat scatterplot!


# Learning Assessment
The chunk below creates a dataframe containing a sample of size 500 from a 
random normal variable, constructs the specified logical vector, takes the 
absolute value of each element of that sample, and produces a histogram of 
the absolute value. The code chunk also finds the median of the sample and
stores it for easy in-line printing.

```{r}
la_df = 
  tibble(
    numeric_samp = rnorm(500, mean = 1),
    greater_0 = numeric_samp > 0,
    abs_val_samp = abs(numeric_samp)
)

ggplot(la_df, aes(x = abs_val_samp)) + geom_histogram()
```

inline code:  

The sample size in the new dataframe is `r nrow(la_df)`.  

The median of the variable containing absolute values is 
`r round(median(pull(la_df, numeric_samp), digits = 2))`.

If I want to talk about `la_df`, i would use the backticks.


# Let's look at formatting

All of this is markdown formatting.  

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_  
**bold**  or  __bold__  
`code`  
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell
